Psych 254 Replication Project Analysis

### 2016-05-12 analysis.Rmd
Start analysis aggregation

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y")
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

@@

```{r}
project_plan <- project_plan_raw %>%
  filter(`Include in final writeup?`==1) 
```

>>>>

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y") # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

@@

```{r}
project_plan <- project_plan_raw %>%
  filter(`include_in_final_writeup`==1) 
```

Read in project_info data from each project

```{r}
errors <- list()# Initialize an error var

all_project_info <- data.frame( # initialize an empty dataframe
  project_key = character()
)

project_keys <- list(project_plan$project_key) # Find user names that are included in analysis
# For each user_

temp_project_keys <- c("smraposo","jmarias","ehermann","mkeil.R")

# Run all respective R code - need loop because project_keys same variable name
for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
  fp <- paste0("project_analyses/",project_key,".R")
  source(fp)
  if(exists("project_info")) { # If has project_info dataframe
    all_project_info <- rbind.fill(all_project_info,project_info) # add to all data
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}

```
